---
title: "Assignment_3_KimKyungA"
author: "Kyung A Kim"
date: '2021 11 6 '
output:
  pdf_document: 
    latex_engine: xelatex
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Introduction

## 1-1. Load the data
First, set working directory of this R project. Next, load the data using _read.csv_ function

```{r}
# set working directory
setwd("D:/대학원/2021-2/1. 수업/R 물류 데이터 분석/3. 과제/Assignment_3_KimKyungA")

# read data set
data <- read.csv("food-price-index-September-2021-index-numbers-csv-tables.csv")
```

## 1-2. Check dataset
After loading dataset, we need to check data whether it contains **NA values**.

```{r}
# check data briefly
head(data,3)
tail(data,3)

str(data)
summary(data)

# check NA values
sum(is.na(data))
colSums(is.na(data))
```

As we can see, we can know that there are NA values in column **Data_value**

## 1-3. Remove NA values

So, by using _complete.cases_ function, we can delete NA values

```{r}
# remove NA values
good <- complete.cases(data)
data1 <- data[good,]

head(data1,3)
```

After removing NA values, check again whether the code I wrote worked well.

```{r}
# check NA values again
sum(is.na(data1))
colSums(is.na(data1))
```

We can find out that all NA values are removed well.

# 2. Data manipulation
To make a tidy data, there are lots of libraries can be used. In this stage, I will use 4 different libraries to manipulate dataset.

## 2-1. Ordering data with plyr library
By using *plyr* library, we can reorder the dataset. So, I use _arrange_ function and reorder dataset in chronological sequence.
```{r}
library(plyr)
arrange(data1, Period)
head(arrange(data1, Period), 30)
tail(arrange(data1, Period), 30)
```

## 2-2. Cutting data with Hmisc library
By using *Hmisc* library, we can cut dataset into few groups. So, I use _cut2_ fuction and cut dataset into 4 groups and look at how many rows are included in each group by using table function
```{r}
library(Hmisc)
# cut the dataset using Data_value column
data1$price_groups <- cut2(data1$Data_value, g=4)
table(data1$price_groups)

# cut the dataset using Period column
data1$PeriodGroups <- cut2(data1$Period, g=6)
table(data1$PeriodGroups)

# or by using mutate fuction, I can get same result as above
data2 <- mutate(data, PeriodGroups=cut2(Period, g=4))
table(data2$PeriodGroups)
```

## 2-3. Melting data with reshape2 library
By using *reshape2* library, I can choose the columns that I want and melt it into more tidy form. So, I choose "Period", "Series_title_1", "Data_value" columns and melt it.
```{r}
library(reshape2)
dataMelt <- melt(data, id=c("Period", "Series_title_1"), measure.vars=c("Data_value"))
head(dataMelt)
tail(dataMelt)
```

## 2-4. Adding new column with dplyr library
By using *dplyr* library, I can make new columns. So I use _mutate_ function to make new column, which name is 'KOR_won'. 'KOR_won' is calculated as Data_value multiplied by 1186.50 which is exchange rate of dollar-won now.

```{r}
library(dplyr)
mutate(data1, KOR_won=Data_value*1186.50)
data2 <- mutate(data1, KOR_won=Data_value*1186.50)
head(data2,5)
```

## 2-5. Changing data into data table form
By using *data.table* library, I can handle data.table form of data. So I change data form into data table and select the columns which I thought is usful.
```{r}
library(data.table)
data3 <- data.table(data2)
data3
tables()
data3[c(1,2), c(2)]
head(data3[, c(2,3,8,11)])

data4 <- data.frame(data3[, c(2,3,8,11)])
head(data4)
```

# 3.Use the factor function for column "Series_title_1" and get the average for each product using the price values in column "Data_value" by sapply function. 

## 3-1. Changing "Series_title_1" into factor

```{r}
# creating factor variable
data2$Series_title_2 <- factor(data2$Series_title_1)
data2$Series_title_3 <- c(as.factor(data2$Series_title_1))

# check data set (factor function and as.factor have same result)
str(data2)
```

## 3-2-1. Get average for each product using the price values in column "Data_value" by sapply function

```{r}
data5 <- split(data2$Data_value, data2$Series_title_2)
data5
sapply(data5, mean)
```

## 3-2-2. Get average for each product using the price values in column "Data_value" by melt, cast function

```{r}
# (2) using melt, cast function
library(reshape2)

dataMelt <- melt(data2, id=c("Series_title_2"), measure.vars=c("Data_value"))
head(dataMelt,3)

average_dataMelt <- dcast(dataMelt, Series_title_2~variable, mean)
average_dataMelt
```


